### 2014-01-27 thesis/src/chapters/chapter-design.tex
Thesis: autonomic container, stub

% darek
\section{Application Platform manager}
w kazdej sekcji opis MAPEK - co monitoruje, w jaki sposob analizuje i planuje, wykonuje

@@

It is highly recommended that sensors and effectors to be linked together, forming manageability capabilities. In other words, property (i.e. CPU) can be read only when it is possible to set it as well.

\subsection{Autonomic controller}
As one can see in XXX, autonomic controller has 4

\subsubsection{Monitoring}

>>>>

\begin{figure}[!ht]
  \begin{center}
    \includegraphics{chapter-design/autonomic-component}
  \end{center}
  \caption{autonomic component}
  \label{img:autonomic-component}
\end{figure}

% darek
\section{Application platform manager}
w kazdej sekcji opis MAPEK - co monitoruje, w jaki sposob analizuje i planuje, wykonuje

@@

It is highly recommended for sensors and effectors to be linked, forming together manageability capabilities. In other words, property (i.e. CPU) can be read only when it is possible to set it as well.

\subsection{Autonomic controller}
Generally speaking, autonomic container controller aims to automate container's management function and externalise its configuration through its interfaces. In order to do achieve that, it implements a control loop that fully covers container life cycle: gathering information about it, analysing it, planning and executing actions on top of that. These four functions along with knowledge necessary to perform them designate modular structure of a controller as shown in figure \ref{img:autonomic-component}.

\subsubsection{Monitoring}
As it was already mentioned, monitoring module aims to gather data from container's sensors. While design of Cloud-SAP doesn't have any specific requirements regarding underlying monitoring mechanism, there are a few aspects that should be taken into consideration:
\begin{asparaenum}
  \item[\textbf{Data filters}]

  \item[\textbf{Persistence}]

  \item[\textbf{Standard compatibility}] Whilst there is no single, industry accepted standard of virtual machine monitoring, there were initiatives such as OCCI \cite{OCCI} that aims to close that gap. Having scaling across multiple cloud instances in mind, it is vital to provide compatibility at a container monitoring level. However, in some cases, standard-defined API may no be sufficient for a specific needs  
\end{asparaenum}
